Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-25 Methods-and-Results.Rmd
table fix

workerMlCor %>%
  kable(
    .,
    caption = "Worker: Multilevel Core Variable Descriptives",
    format = "latex",
    booktabs = TRUE,
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  save_kable("Tables/workerVarDescr.tex")
```

@@

workerOutMlCor %>%
  kable(
    .,
    caption = "Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
    format = "latex",
    booktabs = TRUE,
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  save_kable("Tables/workerOutVarDescr.tex")

>>>>

workerMlCor %>%
  kable(
    .,
    caption = "Worker: Multilevel Core Variable Descriptives",
    format = "latex",
    booktabs = TRUE,
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/workerVarDescr.tex")
```

@@

workerOutMlCor %>%
  kable(
    .,
    caption = "Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
    format = "latex",
    booktabs = TRUE,
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/workerOutVarDescr.tex")
